\documentclass[a4paper,twoside]{report}
% notar que o relatório pode ser frente-e-verso ou apenas uma página por folha

\usepackage{relatorio} % formato ``oficial''
\usepackage[english]{babel} % para que as figuras e secções apareçam em pt
\usepackage[utf8]{inputenc} % Unicode
\usepackage{graphicx} % incluir imagens
\usepackage{url} % typeset URL's
\usepackage{textcomp} % símbolo do euro
\usepackage{multirow} % células com mais que uma linha em tabelas
\usepackage[pdftex,hidelinks]{hyperref}
\usepackage{listings}

\lstset{language=Java,breaklines=true,basicstyle=\scriptsize\ttfamily,frame=single,showstringspaces=false}
\graphicspath{ {./imagens/} }

\begin{document}
\dept{ESTIG - Escola Superior de Tecnologia e Gestão}
\course{Master in Information Systems}

\title{Meta Social Media}

\author{Carlos de Souza Lima}
\secondauthor{Leonardo Leite Meira dos Santos}
%\secauthnum{22222}

\supervisor{Prof. Paulo Matos}
% Coloca a capa, primeira página e outros

\beforepreface

\prefacesection{Abstract}
This research project aims to explore the concept of social meta-network, as a way of integrating social networks, such as Facebook, LinkedIn and others, providing an integrated perspective and transversal functionalities of added value for its users. The present approach uses graph databases. The nodes/vertices of the graph are used to represent people; properties on nodes are used to represent personal information of each individual; the relationships/edges represent directional relationships between individuals according to each social network; and the properties about relationships serve to maintain information about the relationship between individuals for each social network. The model created intends to be a mixed solution focused on relationships by type of social network, referring details to the information existing in the native network itself. Native networks are seen as distinct dimensions in which the present solution makes it possible to relate information between these dimensions, even when there are no relationships between the networks/user in question. It also allows for a more complete perspective of each individual, integrating the professional, playful and other more specialized aspects, which leads to results that are much higher than what can be achieved by looking individually at each network - whether for problems/challenges of centrality/influence, identification, and characterization of communities, identification of similarities, identification of potential relationships, among many other approaches. In practical terms, a considerable asset for marketing purposes.

% Coloca índices
\afterpreface

\bodystart
 
% inclusão do texto, propriamente dito
\include{cap1}
\include{cap2}
\include{cap3}

% listagem de referências
\bibliography{refs}
% estilo de referências. outros valores posíveis são 'plain' e 'abbrv'
\bibliographystyle{ieeetr}

% Apêndice 
%\appendix
%\include{apendice}

\end{document}
